---
title: Epidemic situation in Egypt
author: Ying Zou
date: '2020-09-04'
slug: epidemic-situation-in-egypt
categories: []
tags: []
---


### The overseas epidemic situation is getting worse. In this blog, I will make some simple data analysis on the world epidemic situation and the epidemic situation in Egypt.the total cases is 99280.	[xinhuanet](http://www.xinhuanet.com/english/2020-07/10/c_139201231.htm)


```{r setup, echo=FALSE,message=FALSE}
library(ggplot2)
library(tidyverse)
library(tibble)
library(dplyr)
library(pacman)
p_load(vistime,tidyfst)
library(broom)
library(MASS)
library(kableExtra)


```
### This table Summarized the total confrimed cases by country (top 10).The total number of confirmed cases in Egypt ranks 31st among the total number of confirmed cases in the world.
```{r number, echo=FALSE,warning=FALSE,message=FALSE}
coronavirus <- readr::read_csv(here::here("content/post/data/coronavirus.csv"))
summary_df <- coronavirus %>% 
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(-total_cases) %>%
  # summary_df %>% 
  filter(country%in% c("Egypt","US","Brazil")) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
 summary_df


```

```{r , echo=FALSE,warning=FALSE,message=FALSE}
Egypt_confirmed <- dplyr::filter(coronavirus,country==	"Egypt",type=="confirmed")
Egypt_death<- dplyr::filter(coronavirus,country==	"Egypt",type=="death")
Egypt_recover<- dplyr::filter(coronavirus,country==	"Egypt",type=="recovered")

```


```{r, echo=FALSE,warning=FALSE,message=FALSE}
num_Egypt <- coronavirus %>%
  filter(country == "Egypt") %>%
#  select(date) %>%
  pivot_wider(id_cols = date, names_from = type, values_from = cases) %>%
  arrange(desc(date))
num_Egypt
```


```{r,echo=FALSE,warning=FALSE,message=FALSE}
DT_Egypt <- DT::datatable(num_Egypt, options = list(pageLength = 10))
widgetframe::frameWidget(DT_Egypt, height = 524.08, width = '95%')
```


