---
title: 'Epidemic situation in Pakistan '
author: Ying Zou
date: '2020-09-15'
slug: pakistan
categories: []
tags: []
---


![](https://images.app.goo.gl/F948UcsBdPNWs8Dz7)



## Steady decline in Pakistan's caseload
People from all over the world have been fighting with Covid-19 for several months. A look at the present global Covid-19 trajectory shows that a handful of countries that had reported some of the worst outbreaks in June and July have started witnessing a persistent and steady decline in caseload.Pakistan witnessed a sudden spike in infections and deaths in June, but confirmed cases have gradually declined since then.

We can see the daily new cases and daily death in Pakistan from the plot below,The virus started picking up pace in Pakistan in May, with the country reporting between 989 (May 2) and 3,039 (May 30) cases on a daily basis. The peak hit on June 13 when as many as 6,825 cases were reported in a single day. Since the middle of June, the number of new cases has declined steadily, with the figure falling below 1,000 in August and below 600 in September.(CGTN, 2020).[CGTN](https://news.cgtn.com/news/2020-09-16/Pakistan-s-fight-against-COVID-19-A-success-story--TPi9CHkXbq/index.html)

Recently Pakistan has seen the number of weekly infections steadily decreasing. The reason behind arresting the rise in Covid-19 cases lies in the country’s increased testing capacity in a very short period and setting up a sophisticated tracking system, which included over 10,000 contract workers and more than 3,000 contact tracing teams on the ground. Besides, strict lockdowns in hotspots and hefty fines for violations also played a role.(theindianexpress, 2020).

[theindianexpress](https://indianexpress.com/article/world/countries-where-coronavirus-covid-19-cases-are-dipping-and-the-reasons-6569484/)

```{r setup, echo=FALSE,message=FALSE}
library(ggplot2)
library(tidyverse)
library(tibble)
library(dplyr)
library(pacman)
p_load(vistime,tidyfst)
library(broom)
library(MASS)
library(kableExtra)

```


```{r Daily New Cases in Pakistandata,echo=FALSE,warning=FALSE,message=FALSE}
coronavirusnew <- readr::read_csv(here::here("content/post/data/coronavirusnew.csv"))
num_pakistan <- coronavirusnew %>%
  filter(country == "Pakistan") %>%
#  select(date) %>%
  pivot_wider(id_cols = date, names_from = type, values_from = cases) %>%
  arrange(desc(date))
  num_pic <- subset(num_pakistan,date >=as.Date("2020-02-25")&
           date<as.Date("2020-09-16"))
  databreaks <- seq(as.Date("2020-02-25"),as.Date("2020-09-16"),by='1 week')

```

```{r Daily New Cases in Pakistan,echo=FALSE,warning=FALSE,message=FALSE}
plot1 <- ggplot(num_pic,aes(x=date,y=confirmed))+
  geom_bar(stat='identity',fill = "lightpink")+
  xlab('Date')+ylab('Novel Coronavirus Daily Cases')+
  ggtitle('Daily New Cases in Pakistan')+
  scale_x_date(breaks =databreaks )+
  theme(axis.text = element_text(angle = 30,hjust = 1))

plot2 <- ggplot(num_pic,aes(x=date,y=death))+
  geom_bar(stat='identity',fill = "lightblue")+
  xlab('Date')+ylab('Novel Coronavirus Daily Deaths')+
  ggtitle('Daily New Deaths in Pakistan')+
  scale_x_date(breaks =databreaks )+
  theme(axis.text = element_text(angle = 30,hjust = 1))
  plot1
  plot2
  
#plot_grid(plot1, plot2, labels = "AUTO")
```



## Nearly 96% of Pakistan’s Covid patients have recovered

Nearly 96 per cent of Pakistan's coronavirus patients have made a successful recovery, a status report issued on Wednesday by the country's nerve centre monitoring the pandemic read.

According to the National Command and Operations Centre (NCOC), "290,760 people recovered so far across Pakistan, making it a significant count" and showing that 95.93 per cent of the patients recovered, with 303,089 total cases, of which 5,936 were active ones," Geo news reported.

The NCOC said almost 29,100 tests were carried out over the past 24 hours and 665 people tested positive for the coronavirus.(nationalherald,2020)[nationalherald](https://www.nationalheraldindia.com/international/nearly-96-of-pakistans-covid-patients-have-recovered-report)

The table below shows the number of active cases, deaths, and recovery in Pakistan. We can find that as the epidemic situation in Pakistan improves, more and more people have recovered.







```{r Total Cases in Pakistan,echo=FALSE,warning=FALSE,message=FALSE}
library(plotly)
num_pakistan %>% 
 
  arrange(date) %>%
  mutate(active = confirmed - death - recovered) %>%
  mutate(active_total = cumsum(active),
                recovered_total = cumsum(recovered),
                death_total = cumsum(death)) %>%
  plot_ly(x = ~ date,
                  y = ~ active_total,
                  name = 'Active', 
                  fillcolor = '#1f77b4',
                  type = 'scatter',
                  mode = 'none', 
                  stackgroup = 'one') %>%
  add_trace(y = ~ death_total, 
             name = "Death",
             fillcolor = '#E41317') %>%
  add_trace(y = ~recovered_total, 
            name = 'Recovered', 
            fillcolor = 'forestgreen') %>%
  layout(title = "Distribution of Covid19 Cases in Pakistan",
         legend = list(x = 0.1, y = 0.9),
         yaxis = list(title = "Number of Cases"),
         xaxis = list(title = "Date"))
```

References:

TheIndianExpress. (2020). Five countries where Covid-19 cases are dipping and the reasons why. Retrieved from https://indianexpress.com/article/world/countries-where-coronavirus-covid-19-cases-are-dipping-and-the-reasons-6569484/

CGTNs. (2020). Pakistan's fight against COVID-19: A success story?. Retrieved from https://news.cgtn.com/news/2020-09-16/Pakistan-s-fight-against-COVID-19-A-success-story--TPi9CHkXbq/index.html

Nationalherald. (2020). Nearly 96% of Pakistan’s Covid patients have recovered: Report. Retrieved from https://www.nationalheraldindia.com/international/nearly-96-of-pakistans-covid-patients-have-recovered-report
