---
title: 'Epidemic situation in Pakistan '
author: Ying Zou
date: '2020-09-15'
slug: pakistan
categories: []
tags: []
---

### Steady decline in Pakistan's caseload
People from all over the world have been fighting with Covid-19 for several months. A look at the present global Covid-19 trajectory shows that a handful of countries that had reported some of the worst outbreaks in June and July have started witnessing a persistent and steady decline in caseload.Pakistan witnessed a sudden spike in infections and deaths in June, but confirmed cases have gradually declined since then.

We can see the daily new cases in Pakistan from the plot below,Pakistan has seen the number of weekly infections steadily decreasing. The reason behind arresting the rise in Covid-19 cases lies in the country’s increased testing capacity in a very short period and setting up a sophisticated tracking system, which included over 10,000 contract workers and more than 3,000 contact tracing teams on the ground. Besides, strict lockdowns in hotspots and hefty fines for violations also played a role.
[theindianexpress](https://indianexpress.com/article/world/countries-where-coronavirus-covid-19-cases-are-dipping-and-the-reasons-6569484/)

```{r setup, echo=FALSE,message=FALSE}
library(ggplot2)
library(tidyverse)
library(tibble)
library(dplyr)
library(pacman)
p_load(vistime,tidyfst)
library(broom)
library(MASS)
library(kableExtra)

```


```{r Daily New Cases in Pakistandata,echo=FALSE,warning=FALSE,message=FALSE}
coronavirusnew <- readr::read_csv(here::here("content/post/data/coronavirusnew.csv"))
num_pakistan <- coronavirusnew %>%
  filter(country == "Pakistan") %>%
#  select(date) %>%
  pivot_wider(id_cols = date, names_from = type, values_from = cases) %>%
  arrange(desc(date))
  num_pic <- subset(num_pakistan,date >=as.Date("2020-02-25")&
           date<as.Date("2020-09-16"))
  databreaks <- seq(as.Date("2020-02-25"),as.Date("2020-09-16"),by='1 week')

```

```{r Daily New Cases in Pakistan,echo=FALSE,warning=FALSE,message=FALSE}
ggplot(num_pic,aes(x=date,y=confirmed,fill = "pink"))+
  geom_bar(stat='identity')+
  xlab('Daily cases')+ylab('Novel Coronavirus Daily Cases')+
  ggtitle('Daily New Cases in Pakistan')+
  scale_x_date(breaks =databreaks )+
  theme(axis.text = element_text(angle = 30,hjust = 1))
  
```











